Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-03 vertical-thermal-review.Rmd
remove table S2
closes #57

#SI table numbers
NEON_sites = "S1"
Tealeaves_parameters = "S2"

#SI table captions
NEON_sites_legend = "Table S1. National Ecological Observatory Network (NEON) sites included in the analysis of vertical gradients of key biophysical characteristics"
Tealeaves_parameters_legend <- "Table S2. (Tealeaves parameters)"

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in $T_{leaf}-T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`. Model parameters for biophysical conditions are given in Supplementary Information Table `r Tealeaves_parameters`.](leaf_energy_balance/fig3_leafenergy.png)

@@

`r Tealeaves_parameters_legend`

>>>>

#SI table numbers
NEON_sites = "S1"

#SI table captions
NEON_sites_legend = "Table S1. National Ecological Observatory Network (NEON) sites included in the analysis of vertical gradients of key biophysical characteristics"

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in $T_{leaf}-T_{air}$ in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the tealeaves R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA), as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`.](leaf_energy_balance/fig3_leafenergy.png)

@@

### 2021-09-03 vertical-thermal-review_SI.Rmd
remove table S2
closes #57

Energy balance for a typical overstory sun leaf and understory shade leaf were modeled in the R package *Tleaves* [@muir_tealeaves_2019], parameterized for *Quercus rubra* L. leaves at Harvard Forest, MA, USA (**GEOGRAPHIC COORDINATES).
Parameters are presented in Table `r Tealeaves_parameters`.

@@

\newpage
# `r Tealeaves_parameters_legend `

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
parameters_table <- read.csv("NEON_height_profiles/HARV_neon_stats_handedit.csv", stringsAsFactors = FALSE, check.names = FALSE)
parameters_table <- parameters_table[which(parameters_table$include==1),c(9, 1, 3)] #select and order columns for inclusion
ft <- flextable(parameters_table)
ft <- autofit(ft)
ft
```

>>>>

Energy balance for a typical overstory sun leaf and understory shade leaf were modeled in the R package *Tleaves* [@muir_tealeaves_2019], parameterized for *Quercus rubra* L. leaves at Harvard Forest, MA, USA (42.5369, -72.17266).

@@
